Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-02-13 paper/1_Initial/manuscript.qmd
uninformative  sentence
reorganize

Although the use of subjective self-report questionnaires to measure deeply embodied functions might seem paradoxical at first, recent redefinitions of interoception emphasize the role of high-level and metacognitive elaboration of interoceptive information.
These redefinitions provide theoretical grounding to support the idea that some facets of interoception, including participants' metacognitive beliefs, can be assessed subjectively [@khalsa2018interoception; @suksasilp2022towards].

This approach offers useful and interesting measures [@murphy2019; @lin2023].

<!-- lack of correlation between objective and subjective measures + lack of correlation between self-report measures-->

The notion that self-reports might not reflect the same processes as other interoception measures is important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures].
While few studies have explored the correlation between objective interoceptive measures,  such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological], and correspondent self-report measures, existing findings typically show weak or no correlations [e.g., task-based accuracy vs. self-reported accuracy, @murphy2019; @brand2023].

>>>>

Although the use of subjective self-report questionnaires to measure deeply embodied functions might seem paradoxical at first, recent redefinitions of interoception emphasize the role of high-level and metacognitive elaboration of interoceptive information.
These redefinitions provide theoretical grounding to support the idea that some facets of interoception, including participants' metacognitive beliefs, can be assessed subjectively [@khalsa2018interoception; @suksasilp2022towards].
<!-- lack of correlation between objective and subjective measures + lack of correlation between self-report measures-->
Moreover, the notion that self-reports might not reflect the same processes as other interoception tasks might be important to contextualize the apparent lack of convergence between measures in the field [@desmedt2022measures]. For instance, existing findings typically show weak or no correlations between questionnaires and objective measures [including for measures of the same theorethical dimensions, e.g., task-based accuracy vs. self-reported accuracy, @murphy2019; @brand2023], such as the Heartbeat Counting Task [HCT, @schandry1981heart] and the Heartbeat Detection Task [HDT, @kleckner2015methodological].
